---
title: "Network Analysis of Multivariate Data: Streamlined Gaussian Graphical Model"
output: html_notebook
---
  
  <!-- [R Markdown](http://rmarkdown.rstudio.com) -->
  <!-- Try executing this chunk by clicking the Run: *Cmd+Shift+Enter*.  -->
  <!-- Insert Chunk: *Cmd+Option+I* -->
  <!-- Preview: *Cmd+Shift+K* -->
  <!-- Comment: *Cmd+Shift+C* -->
  
This is an R Markdown Notebook explaining the Mental Health code in Network Analysis of Multivariate Data

First, let's import the necessary packages
```{r}
library(ggplot2)
library(dplyr)
library(mlVAR)
library(qgraph)
library(bootnet)
library(reshape)
library(viridis)
#install.packages("lm.beta") # Added
library(lm.beta)
library(lubridate)
library(graphicalVAR)
library(igraph)
#install.packages("vars")
#library(vars)
```

Now, let us set our working directory to where we have our files. Well also set ourselves up for the figure and data directory
Below, we load our data table and get our variables.  

```{r}
Daily_Data <- read.csv("CrossCheck_Daily_Data.csv")
print(Daily_Data)
varLabs <- c('ema_CALM', 'ema_SOCIAL', 'ema_SLEEPING', 'ema_THINK', 'ema_HOPEFUL',
       'ema_VOICES', 'ema_SEEING_THINGS', 'ema_STRESSED', 'ema_HARM',
       'ema_DEPRESSED')
Daily_Data <- na.omit(Daily_Data[c('study_id', 'ema_CALM', 'ema_SOCIAL', 'ema_SLEEPING', 'ema_THINK', 'ema_HOPEFUL', 'ema_VOICES', 'ema_SEEING_THINGS', 'ema_STRESSED', 'ema_HARM', 'ema_DEPRESSED')]) # Get rid of non-data days
names(Daily_Data)[names(Daily_Data) == 'study_id'] <- 'id'
ids <- unique(Daily_Data$id)
```

```{r}
get_Network_2 <- function(data, id_name) {
  vars <- c(colnames(Daily_Data)) # These are the variables we want to investigate
  # Alpha to detrend:
  alpha <- 0.05
  user_3 <- Daily_Data
  # names(Daily_Data)[names(Daily_Data) %in% vars] <- varLabs
  
  varLabs <- vars
  varLabs <- varLabs[!varLabs %in% c("id")]
  needed_vars <- varLabs
  Needed_df = user_3[needed_vars]
  
  p_values <- data.frame(
  var = c("day")
  )
  
  # Also empty data frame list for test statistics:
  testStatistics <- list()
  coefficients <- list()
  stdcoefficients <- list()
  
  # Data frame to store detrended data:
  data_detrended <- Needed_df
  
  new_vars <- varLabs[!varLabs %in% c("day")]
  data_detrended = data_detrended[new_vars]
  varLabs <- new_vars
  
  # -------------------------------------------------------------------------
  # ------------------------ 3. Here we detrend data ------------------------
  # -------------------------------------------------------------------------
  for (v in seq_along(varLabs)){
    formula <- as.formula(paste0(varLabs[v], " ~ 1 + day")) # 
    lmRes <- lm(formula, data = Needed_df)
    # Fixed effects:
    fixed <- coef(lmRes) # Get the model coefficients
    # make zero if not significant at alpha
    p_values[[varLabs[v]]] <- anova(lmRes)[["Pr(>F)"]][1] # Anova, difference of means
    # A table with p values for each ema collected 
    if (p_values[[varLabs[v]]][1] > alpha){
      fixed[2] <- 0
    }  
  
    # Detrend data:
    data_detrended[,varLabs[v]] <- Needed_df[,varLabs[v]] - (fixed[1] + fixed[2] * Needed_df[["day"]])
    
    ids <- rownames(anova(lmRes))
    # "day"          "factor(beep)" "Residuals"
    testStatistics[[v]] <- cbind(data.frame(var = varLabs[v], effect = ids), anova(lmRes))
    
    coefficients[[v]] <- data.frame(
      var = varLabs[v],
      type = names(coef(lmRes)),
      coef = coef(lmRes),
      std = coef(lm.beta(lmRes)) # Standardized regression coefficients = lm.beta
    )
  }
  
  # -------------------------------------------------------------------------
  # ------------------ 4. Here we estimate network models ------------------
  # -------------------------------------------------------------------------
  
  data_detrended[['id']] <- rep(c(id_name), times=nrow(data_detrended))
  
  # Estimate network using multilevel VAR model
  res <- graphicalVAR(data_detrended,
               vars = varLabs,
               idvar='id',
               gamma = 0.5,
               lags = 1)
  
  # cont <- getNet(res, "contemporaneous", layout = "spring", nonsig = "hide", rule = "and")
  return(res)
}
```

Here you can choose which patient to get the network from in c(user_name)
```{r}
for (id_val in c(-1)){
  Daily_Data <- subset(Daily_Data, id %in% c(id_val)) # Can't use id_val = id here *oof*
  Daily_Data$day <- seq.int(nrow(Daily_Data))
  res <- get_Network_2(Daily_Data, id)
  plot(res, "PCC", layout = "circle")
  plot(res, "PDC", layout = "circle")

}
```
